Univalent Universes and Completness of Reversible Programs

### 2017-02-10 upi.tex
fixed truncation

\begin{itemize}
\item Let $\mathcal{U}$ be the univalent subuniverse generated by $0$, $1$, $+$, and $*$ suitably 1-truncated.
\item Let $\Pi$ be the previously  described reversible programming with 1-paths and 2-paths
\item We conjecture that $\Pi$ includes codes for \emph{all} paths in $\mathcal{U}$
\end{itemize}

@@

We assume an ambient univalent universe defined like in the HoTT book and including dependent pairs, a unit type, coproducts, identity types, and constants $\textsc{funext}$ and $\textsc{univalence}$. Our universe $\mathcal{U}$ is the subuniverse of this ambient universe defined as $\Sigma_{X:\mathbf{Type}} \| X \equiv \mathbb{2} \|_1$ where:

@@

\item $\| A \|_1$ is the 1-truncation of $A$ defined as follows: for all $x,y:A$ and $p,q : x \equiv y$ and $\alpha,\beta : p \equiv q$, we have $\alpha=\beta$.

>>>>

\begin{itemize}
\item Let $\mathcal{U}$ be the univalent subuniverse generated by $0$, $1$, $+$,
  and $*$ suitably truncated.
\item Let $\Pi$ be the previously  described reversible programming with 1-paths and 2-paths
\item We conjecture that $\Pi$ includes codes for \emph{all} paths in $\mathcal{U}$
\end{itemize}

@@

We assume an ambient univalent universe defined like in the HoTT book and including dependent pairs, a unit type, coproducts, identity types, and constants $\textsc{funext}$ and $\textsc{univalence}$. Our universe $\mathcal{U}$ is the subuniverse of this ambient universe defined as $\Sigma_{X:\mathbf{Type}} \| X \equiv \mathbb{2} \|$ where:

@@

\item $\| A \|$ is the propositional truncation of $A$ defined as follows: for
  any $x:A$ we have $|x| : \|A\|$, and for any $x,y : \|A\|$, we have $x \equiv y$.
